Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
intro: order of tools

We have implemented our reduction technique in a tool called
\telatko. We show that the tool can reduce acceptance marks in
automata produced by Delag~\cite{muller.17.gandalf},
ltl3tela~\cite{major.19.atva}, Rabinizer~4~\cite{kretinsky.18.cav},
and Spot~\cite{duret.16.atva2}.  While the reduction is relatively
modest for TELA produced by \texttt{ltl3tela} and Spot,
it is substantial for automata produced by tools of the Owl library.

>>>>

We have implemented our reduction technique in a tool called
\telatko. We show that the tool can reduce acceptance marks in
automata produced by Delag~\cite{muller.17.gandalf},
Rabinizer~4~\cite{kretinsky.18.cav} (both included in the Owl library),
Spot~\cite{duret.16.atva2}
and \texttt{ltl3tela}~\cite{major.19.atva}.  While the reduction is relatively
modest for TELA produced by \texttt{ltl3tela} and Spot,
it is substantial for automata produced by tools of the Owl library.
